Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparative\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-09 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

\begin{abstract}
%Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost. The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained. Commercial equipment data is provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of seven different intricate case studies.
In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends in energy access still fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate or to size electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. The use of formal methods in electrical systems is a new subject, with published research spanning only the last four years. Moreover, the use of automated synthesis in order to obtain optimal sizing of solar photovoltaic systems has never been done before; this is our major goal: a sound, automated approach to obtaining optimal sizing of stand-alone photovoltaic systems using program synthesis. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach, with two phases linking the technical and the cost analysis. First, we synthesize a feasible candidate based on power reliability, but which may not attain the lowest cost. Second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking. If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution. Experimental results using seven case studies demonstrate that we can produce optimal solution within an acceptable run-time. We also present a comparison with a specialized simulation tool over real photovoltaic systems in order to show the effectiveness of our approach.
\keywords{Automated verification  \and Model Checking \and Electric systems \and Solar photovoltaic systems.}
\end{abstract}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
the seamless integration of computational  and  physical  components~\cite{NSF2015}. 
During operation, such components must frequently adapt to the executing environment changes 
faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
%Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
%unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
%
%While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. 
Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS. These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}. Energy production, distribution, and optimization are all CPS problems~\cite{UC}.

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}. To provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}. %; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.

@@

Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}. %However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. 
Related to past work using formal methods based on \textit{symbolic model checking} and its application to electric systems: in $2015$ an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}; in $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}; in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}; and finally, in $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}. However, formal methods and its application to synthesize PV systems are still unexplored in literature.

@@

Our work makes two major contributions. Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically their use in synthesizing PV sizing is unprecedented. %Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. 
Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.

%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:AutomatedVerification}
%-----------------------------------------------------------
%
%-----------------------------------------------------------
\subsection{Program Synthesis}
\label{sec:ProgramSynthesis}
%-----------------------------------------------------------
%
The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$. In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}. As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely. CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.

The correctness specification $\sigma$ provided to our program synthesizer is of the form $\exists \vec{F} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers. The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part. Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.

In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\columnwidth]{fig2_rev.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}
%
One may notice that each iteration of the CEGIS loop adds a new input to the finite set $INPUTS$, which is then used for synthesis.  Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists and our synthesis engine can then conclude that no feasible equipment combination was found. At this specific automated formal synthesis of PV systems, we use a variant of CEGIS, where in each iteration we increase the expected cost of PV systems and this controls the {\sc verify} phase and the search by the optimal sizing.  %however, $\mathcal{D}$ can represent a large number of elements for the finite set  and our synthesis engine can then conclude that no feasible equipment combination was found. 
%In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}. In addition to that, a pre-processing stage could also figure as another block in the scheme shown in Fig. \ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.

/////
Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted. If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost. Note that in this study, our focus is not on new criteria or even optimization objectives. Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods. 
////
Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{iet-cps.2018.5006}; here we have used software verifiers based on SMT solvers: %Here we used software model checking techniques implemented by different tools: 
CPAChecker~\cite{Beyer2011}, CBMC~\cite{Kroening}, and ESBMC~\cite{esbmc2018}.

\textbf{CPAchecker}~\cite{LMU2019} is a state-of-the-art model checker, awarded with the golden medal at the annual competition in software verification: Automatic program verification requires a choice between precision and efficiency. The more precise a method, the fewer false positives it produces, but also the more expensive it is, and thus applicable to fewer programs. Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking. To experiment with the trade-off and to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analysis. Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analysis expressed in the CPA framework. In terms of the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT (Satisfiability Modulo Theories) solvers and interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver~\cite{Beyer2011}.

The C Bounded Model Checker (\textbf{CBMC}) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}. CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports SAT and SMT solvers to discharge verification conditions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$). 
For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
\begin{figure}[h]
\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}
\\
%
The sizing check stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice. 
%
Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\ref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows

@@

\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.

@@

\begin{equation}
\label{eq:NTPmin}
N_{TPmin} = \frac{E_{corrected}}{E_{p}}.
\end{equation}

@@

\begin{equation}
\label{eq:NPSmin}
\frac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \frac{V_{mppt,max}}{V_{maxPower,TempMin}},
\end{equation}
\begin{equation}
\label{eq:NPPmin}
N_{PPmin} = \frac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
\end{equation}
\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
Regarding batteries, we must first define the total capacity of the battery bank, which can be described as
\begin{equation}
\label{eq:Cbank}
C_{bank} = \frac{E_{corrected} \times autonomy}{V_{system} \times DOD},
\end{equation}
\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).
Secondly, the total (minimum) number of batteries is computed as 
\begin{equation}
\label{eq:Nbtotal}
N_{B}total = N_{BS}min \times N_{BP}min = \frac{V_{system}}{V_{bat}} \times \frac{C_{bank}}{Battery \, Capacity}.
\end{equation}

@@

\begin{equation}
\label{eq:vcvsystem}
V_{c} = V_{system}.
\end{equation}

@@

\begin{equation}
\label{eq:iscamb}
I_{sc,amb} = \frac{G}{G_{ref}} \left[I_{sc,ref} +  \mu_{I} \times (T-25) \right]. 
\end{equation}

@@

\begin{equation}
\label{eq:vindc} 
V_{in}DC = V_{system}.
\end{equation}

>>>>

\begin{abstract}
%Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost. The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained. Commercial equipment data is provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of seven different intricate case studies.
In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends in energy access still fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate or to size electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. The use of formal methods in electrical systems is a new subject, with published research spanning only the last four years. Moreover, the use of automated synthesis in order to obtain optimal sizing of solar photovoltaic systems has never been done before; this is our major goal: a sound, automated approach to obtaining optimal sizing of stand-alone photovoltaic systems using program synthesis. We propose a variant of the counterexample guided inductive synthesis (CEGIS) approach, with two phases linking the technical and the cost analysis. First, we synthesize a feasible candidate based on power reliability, but which may not attain the lowest cost. Second, the candidate is then verified iteratively with a lower bound cost via symbolic model checking. If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution. Experimental results using seven case studies demonstrate that we can produce optimal solution within an acceptable run-time. We also present a comparison with a specialized simulation tool over real photovoltaic systems in order to show the effectiveness of our approach.
\keywords{Automated verification  \and Model Checking \and Electric systems \and Solar photovoltaic systems.}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
the seamless integration of computational  and  physical  components~\cite{NSF2015}. 
During operation, such components must frequently adapt to the executing environment changes 
faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
%Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
%unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
%
%While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. 
Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis. % with the goal of synthesizing correct-by-construction implementations of CPS. 
These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}.

Energy production, distribution, and optimization are all CPS problems~\cite{UC}. Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}. To provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}. %; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.

@@

Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}. %However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. 
Related to the use of formal methods based on \textit{symbolic model checking} and its application to electric systems: in $2015$ an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}; in $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}; in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}; and finally, in $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}. However, formal methods and its application to synthesize PV systems are still unexplored in literature.

@@

Our work makes two major contributions. \textbf{Firstly}, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically their use in synthesizing PV sizing is unprecedented. %Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. 
\textbf{Secondly}, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.

%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:AutomatedVerification}
%-----------------------------------------------------------
%In this section, we present our theory and methodology to obtain the optimal sizing of stand-alone solar PV systems through program synthesis. In particular, 
Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone PV system, which shows the traditional techniques (manual and simulation) and the proposed automated synthesis. Note that the input information is the same for all the methods: weather data, price information, design requirements, as load curve and power demand, and design assumptions) except for the automated synthesis where we also define the bound $k$ to restrict the design-space search. Related to the output presented by both techniques, all of them produce a SUCCESS or FAIL result considering a feasible technical solution with the lowest cost. On the one hand, when done by simulation we get a report or graphical result; on the other hand, the automated synthesis technique, which is a mathematical reasoning of a model, presents a counterexample with the optimal solution stored in variables. Furthermore, 
%as described in this section, 
the design-space coverage during the optimal sizing search is sound and complete when using automated synthesis.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{optimalsizingprocess3}
\centering
\caption{Comparison of optimal sizing methods.}
\label{fig:optimization}
\end{figure}

%-----------------------------------------------------------
\subsection{Program Synthesis}
\label{sec:ProgramSynthesis}
%-----------------------------------------------------------
Program synthesis addresses an age-old problem in computer science: can a computer program itself?~\cite{Bornholt2019}. Before the computer can automatically generate a program, it is necessary to give it a specification of what the program should do. The specification needs to describe the program's desired behavior to ensure that the program does what it intends.

The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$. In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}. As a result, a given candidate program $p$ is iteratively refined, to match $\sigma$ more closely. CEGIS represents one of the most popular approaches to program synthesis currently used in practice for cyber-physical problems~\cite{Abateetal2017}, as energy production, distribution, and optimization. Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} illustrates the underlying architecture. Note that CEGIS has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}. %from model checking.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.75\columnwidth]{fig2_rev2.jpg}
	\caption{CEGIS adapted to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}

The correctness specification $\sigma$ provided to our program synthesizer is of the form $\exists \vec{F} . \forall \vec{x}. \sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free (QF) formula typically supported by SMT solvers. The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part. Examples of specifications used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specifications and prices from different manufacturers and models.

In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, regarding traditional CEGIS method, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs}, which is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc Synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc Verify} in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, in the CEGIS traditional method, additional information is provided to the phase {\sc Synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again.

One may notice that each iteration of the traditional CEGIS loop adds a new input to the finite set $INPUTS$, which is then used for synthesis. Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc Synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists, and our synthesis engine can then conclude that no feasible equipment combination was found.

In our variant CEGIS method, there exist four distinct differences related to the traditional CEGIS: 
(1) there exists no test vector and every candidate is generated during the run-time in the {\sc Synthesize} phase and sent to the {\sc Verify} phase; 
(2) if the {\sc Verify} phase is unsuccessful, then a new candidate is generated by {\sc Synthesize} and 
(3) the lower bound of the {\sc Verify} phase is incremented to search for the lowest cost; 
(4) as a result, there exists no refinement from the {\sc Verify} phase back to the {\sc Synthesize} phase, i.e., 
a new counterexample is not added to the {\sc input} set since a failure during the {\sc Verify} phase will only discard a given candidate, which could be feasible in the next iteration with a new lower bound.

Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications %, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{iet-cps.2018.5006}; 
here we have used software verifiers based on SMT solvers: %Here we used software model checking techniques implemented by different tools: 
CPAChecker~\cite{Beyer2011}, CBMC~\cite{Kroening}, and ESBMC~\cite{esbmc2018}.

\textbf{CPAchecker}~\cite{LMU2019} is a model checker awarded with the golden medal at the annual competition in software verification: Automatic program verification requires a choice between precision and efficiency. The more precise a method, the fewer false positives it produces, but also the more expensive it is, and thus applicable to fewer programs. Historically, this trade-off was reflected in two major approaches to static verification: program analysis and model checking. To experiment with the trade-off and to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analysis. Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analysis expressed in the CPA framework. In terms of the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver~\cite{Beyer2011}.

The C Bounded Model Checker (\textbf{CBMC}) falsifies assertions in C programs or proves that they are safe if a completeness threshold is given~\cite{Kroening}. CBMC implements a bit-precise translation of a C program, annotated with assertions and with loops unrolled up to a given depth, into a logical formula. If the formula is satisfiable, then a failing execution that leads to a violated assertion exists~\cite{Kroening}. CBMC's verification flow can be summarized in three stages: (i) Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; (ii) Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; (iv) Back-end: supports Boolean Satisfiability (SAT) and SMT solvers to discharge verification conditions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$). 
For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.

\begin{figure}[h]
\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}

The sizing check stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice. 
%
Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\ref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows

@@

\noindent where the solar irradiance is expressed in terms of $kWh/m^{2}$ and depends on the site where the PV system will be deployed; 
the PV panel area is given in $m^{2}$ and corresponds to the size of one PV panel, and $\eta_{p}$ represents the PV panel efficiency.

@@

\begin{equation}
\label{eq:NTPmin}
N_{TPmin} = \frac{E_{corrected}}{E_{p}}.
\end{equation}

@@

\begin{equation}
\label{eq:NPSmin}
\frac{V_{mppt,min}}{V_{maxPower,TempMax}} \leq N_{PSmin} \leq \frac{V_{mppt,max}}{V_{maxPower,TempMin}},
\end{equation}

\begin{equation}
\label{eq:NPPmin}
N_{PPmin} = \frac{P_{total}}{Number\,Panels\,Series \times P_{max,ref}},
\end{equation}

\noindent where $V_{mppt,max}$ is the maximum operation voltage and $V_{mppt,min}$ is the minimum operation voltage of the charge controller; $V_{maxPower,TempMax}$ and $V_{maxPower,TempMin}$ are the maximum power voltage from the PV module considering the maximum and minimum operational temperature, respectively; $P_{total}$ is the total power demanded from the PV system and $P_{max,ref}$ is the power supplied from one PV panel in $Watts$.
%, $ V_{system} $ is the DC voltage of the bus, normally $12$, $24$ or $48$ V.
%
Regarding batteries, we must first define the total capacity of the battery bank, which can be described as

\begin{equation}
\label{eq:Cbank}
C_{bank} = \frac{E_{corrected} \times autonomy}{V_{system} \times DOD},
\end{equation}

\noindent where the variable $autonomy$ is a design definition; % and normally has a value ranging from $6$ to $48$h; 
$ V_{system} $ is the DC voltage of the bus, and $ DOD $ is the battery deep of discharge (considered of maximum of 25\% here).

Secondly, the total (minimum) number of batteries is computed as 
\begin{equation}
\label{eq:Nbtotal}
N_{B}total = N_{BS}min \times N_{BP}min = \frac{V_{system}}{V_{bat}} \times \frac{C_{bank}}{Battery \, Capacity}.
\end{equation}

@@

\begin{equation}
\label{eq:vcvsystem}
V_{c} = V_{system}.
\end{equation}

@@

\begin{equation}
\label{eq:iscamb}
I_{sc,amb} = \frac{G}{G_{ref}} \left[I_{sc,ref} +  \mu_{I} \times (T-25) \right]. 
\end{equation}

@@

\begin{equation}
\label{eq:vindc} 
V_{in}DC = V_{system}.
\end{equation}
